---
title: "Pitching a Novel Way to Calculate Chicken Weight"
author: "Xavier"
date: "2023-09-09"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What do we need to know? 
- The age of the chicken
- The specific diet of the chicken

## What will the app tell you?

1. The expected weight of the chicken
2. The expected growth trajectory in the next few days 

## An Example of the Output, for Chicken with Diet 1
```{r , echo = F, message=FALSE, warning=FALSE}
    library(dplyr)
    library(datasets)

    model1 <- lm(weight ~ Time, data = subset(ChickWeight, Diet == 1))
    plot(weight ~ Time, data = subset(ChickWeight, Diet == 1),
                 xlab = "Age of Chicken in Days", 
                 ylab = "Expected Weight", bty = "n", pch = 16,
                 xlim = c(0, 22))
            abline(model1, col = "red", lwd = 2)
```

## Why should we care? 
Because using this app you can easily evaluate of your chicken are performing better or worse than average, and make adjustments accordingly! 
